Survey paper tables and figures

### 2021-10-16 survey/code/paper-tables.Rmd
Add READMEs, license, and missing data file
The file has to be compressed because GitHub has a 100mb file size
limit. Fortunately R can decompress the file automatically.

# SVI
svi <- read.csv("data/SVI2018_US_COUNTY.csv") %>%
  mutate(SVI_cat = case_when(RPL_THEMES >= 0.75 ~ "1st quartile",
                             RPL_THEMES >= 0.5 & RPL_THEMES < 0.75 ~ "2nd quartile",
                             RPL_THEMES >= 0.25 & RPL_THEMES < 0.5 ~ "3rd quartile",
                             RPL_THEMES < 0.25 ~ "4th quartile"),
         FIPS = sprintf("%05d", FIPS)) %>%
  select(FIPS, SVI_cat)
```

>>>>

# Centers for Disease Control and Prevention/Agency for Toxic Substances and
# Disease Registry/Geospatial Research, Analysis, and Services Program.
# CDC/ATSDR Social Vulnerability Index 2018 Database US.
# https://www.atsdr.cdc.gov/placeandhealth/svi/data_documentation_download.html
svi <- read.csv("data/SVI2018_US_COUNTY.csv") %>%
  mutate(SVI_cat = case_when(RPL_THEMES >= 0.75 ~ "1st quartile",
                             RPL_THEMES >= 0.5 & RPL_THEMES < 0.75 ~ "2nd quartile",
                             RPL_THEMES >= 0.25 & RPL_THEMES < 0.5 ~ "3rd quartile",
                             RPL_THEMES < 0.25 ~ "4th quartile"),
         FIPS = sprintf("%05d", FIPS)) %>%
  select(FIPS, SVI_cat)
```
